Supplementary Information

### 2021-08-10 doc/manuscript/ForestGEO_treerings.Rmd
Update ForestGEO_treerings.Rmd
#138

Growth rate -- whether measured as RW, BAI, or $\Delta$AGB -- varied with DBH for most species at all sites (Fig. `r size`).
Because the effects of calendar year could not be evaluated for all species (Fig. `r SummaryFigure`), the DBH trends described here refer to models without year. 
Relationships between growth rate and DBH were nonlinear for the majority of site-species combinations (`r round(n_spst_RW_DBH_bm/ n_spst_DBH_analyzed*100)` - `r round(n_spst_dAGB_DBH_best_model/ n_spst_DBH_analyzed*100)`% depending on growth metric; Fig. `r size`).

>>>>

Growth rate -- whether measured as RW, BAI, or $\Delta$AGB -- varied with DBH for most species at all sites (Fig. `r size`).
Because the effects of calendar year could not be evaluated for all species (Fig. `r SummaryFigure`), the DBH trends described here refer to models without year. 
Relationships between growth rate and DBH had second-order terms for the majority of site-species combinations (`r round(n_spst_RW_DBH_bm/ n_spst_DBH_analyzed*100)` - `r round(n_spst_dAGB_DBH_best_model/ n_spst_DBH_analyzed*100)`% depending on growth metric; Fig. `r size`).
